Pathways to Early Vocabulary Acquisition

### 2024-12-03 paper/paper.qmd
Typo updated.

---
title: "Pathways to Early Vocabulary Acquisition"
subtitle: "Mapping English Language Development Trajectories in Children Aged 16–30 Months"
author: Yongqi Liu
thanks: "Code and data are available at: [Early Vocabulary Acquisition Pathway](https://github.com/Cassieliu77/Early_Vocabulary_Acquisition_Pathway.git)"
date: today
date-format: long
abstract: "This study examines vocabulary acquisition in children aged 16–30 months using data from the Word Bank and MacArthur-Bates Communicative Development Inventories. Age is the strongest predictor, with vocabulary size increasing consistently and foundational categories like Function Words, Living Things, and Objects showing higher predicted probabilities, indicating their universal acquisition. Complex categories such as Sensory Words, Adjectives, and Places exhibit broader distributions and lower probabilities, reflecting their reliance on contextual understanding and cognitive complexity. These findings underscore age-specific patterns in vocabulary growth and the need for targeted interventions to support diverse word categories learning."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

This study utilizes the Word Bank R package from @wordbankr, which archives data from @cdi, to investigate vocabulary development in early childhood. By employing a logistic regression model, the research also estimates the likelihood of achieving a high vocabulary score using predictors such as age, norming status, and lexical categories. This model serves as a tool to explore how these factors collectively influence children’s vocabulary acquisition trajectories.

@@

```{r}
#| label: tbl-data
#| tbl-cap: Cleaned Word Bank Dataset
#| echo: false

>>>>

---
title: "Pathways to Early Vocabulary Acquisition"
subtitle: "Mapping English Language Development Trajectories in Children Aged 16–30 Months"
author: Yongqi Liu
thanks: "Code and data are available at: [Early Vocabulary Acquisition Pathway](https://github.com/Cassieliu77/Early_Vocabulary_Acquisition_Pathway.git)"
date: today
date-format: long
abstract: "This study examines vocabulary acquisition in children aged 16–30 months using data from the Wordbank and MacArthur-Bates Communicative Development Inventories. Age is the strongest predictor, with vocabulary size increasing consistently and foundational categories like Function Words, Living Things, and Objects showing higher predicted probabilities, indicating their universal acquisition. Complex categories such as Sensory Words, Adjectives, and Places exhibit broader distributions and lower probabilities, reflecting their reliance on contextual understanding and cognitive complexity. These findings underscore age-specific patterns in vocabulary growth and the need for targeted interventions to support diverse word categories learning."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

This study utilizes the Wordbank R package from @wordbankr, which archives data from @cdi, to investigate vocabulary development in early childhood. By employing a logistic regression model, the research also estimates the likelihood of achieving a high vocabulary score using predictors such as age, norming status, and lexical categories. This model serves as a tool to explore how these factors collectively influence children’s vocabulary acquisition trajectories.

@@

```{r}
#| label: tbl-data
#| tbl-cap: Cleaned Wordbank Dataset
#| echo: false
